An Airdrop That Preserves Recipient Privacy

### 2019-01-19 paper/defs.tex
small clarification in defs

In a private airdrop scheme PAD, a \emph{sender} \Sr creates a \emph{token}
    for a \emph{recipient} \Rt whose key pair is $(\PK, \SK)$, and posts
    this token in a transaction on a blockchain.
To claim the output of the transaction, \Rt generates a signature on a message
    indicating that the token is spent, and posts this message and signature
    to the blockchain.
Finally, any \emph{verifier} \Vr can check the signature on the message
    and the token.

\paragraph{Syntax} PAD is a triple of efficient algorithms:
%
\begin{itemize}
\item $\text{sendTokens}(\PK) \to (c, s)$:
%
\Sr generates token $c$ and secret $s$, posts $c$ publicly, and sends $s$
    to \Rt via some private channel.
%To send a \emph{token} $c$ to a \emph{recipient} \Rt whose key is $(\PK,
%    \SK)$, a \emph{sender} \Sr generates $c$ to be posted on a blockchain,
%    plus a \emph{secret}~$s$ given to \Rt via some private channel.
\unskip\footnote{For example, a encryption of $s$ under $\PK$ can be posted
    to a public messageboard. Note, however, that the posted ciphertext
    should not be publicly associated with the token $c$.}
%\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}

>>>>

\paragraph{High-level description} In a private airdrop, a \emph{sender} \Sr creates a \emph{token}
    for a \emph{recipient} \Rt whose public key is $\PK$, and posts
    the token in a transaction on a blockchain.
To claim the transaction's value, \Rt generates a new transaction and
    uses the token and corresponding secret key $\SK$ to generate a signature; it posts the
    new transaction and the signature to the blockchain.
Any \emph{verifier} \Vr can check the signature on the transaction
    using the token, \emph{without} learning $\PK$.

\paragraph{Syntax} A private airdrop scheme PAD is a triple of efficient algorithms:
%
\begin{itemize}
\item $\text{sendTokens}(\PK) \to (c, s)$:
%
\Sr generates token $c$ and secret $s$, then posts $c$ publicly and sends $s$
    to \Rt via some private channel.
%To send a \emph{token} $c$ to a \emph{recipient} \Rt whose key is $(\PK,
%    \SK)$, a \emph{sender} \Sr generates $c$ to be posted on a blockchain,
%    plus a \emph{secret}~$s$ given to \Rt via some private channel.
\unskip\footnote{For example, a encryption of $s$ under $\PK$ can be posted
    to a public messageboard. Note, however, that the posted ciphertext
    must not publicly associate $\PK$ with the token $c$.}
%\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}
